### 2021-01-24 research project/sections/Background.tex
worked on rp

For the sake of this paper, two different methods with similar 
convergence rates but different approaches have been chosen for 
comparison, the process for the original discovery of these methods
will be explained. The two methods in question are one based on 
the infinite series definition of an inverse trigonometric function 
and one where the value is derived using geometry, by mathematician 
Viète. These two mathematical methods were chosen as they are both 
represent a first occurence in mathematics: Madhava was the first to 
find the series notation of the $\arctan$ function and Viète was one 
of the first mathematicians to use an infinite series in calculation.

@@

So it can be written that, by definition, the ratio of 
the area of an $n$-gon

@@

Which through the trigonometric identity $\sin{2 \alpha} = 2\sin{\alpha} \cos{\alpha}$ can 
be simplified to:

@@

There is however, a neater expression for this same formula. 
To simplify to it, firstly we let $U_{0} = \cos{\alpha}$. Then, we 
define $U_{1} = cos{\frac{\alpha}{2}}$, following the formula stated 
before.

>>>>

For the sake of this paper, two different methods with similar 
convergence rates but different approaches have been chosen for 
comparison, the process for the original discovery of these methods
will be explained. The two methods in question are one based on 
the infinite series definition of an inverse trigonometric function 
and one where the value is derived using geometry, by mathematician 
Viète. These two mathematical methods were chosen as they are both 
represent a first occurence in mathematics: Madhava was the first to 
find the series notation of the arctangent function and Viète was one 
of the first mathematicians to use infinite series in his calculation.

@@

So it can be written that, by definition, the ratio of 
the area of an $n$-gon to one of a $2n$-gon is

@@

Which through the trigonometric identity $\sin{2 \theta} = 2\sin{\theta} \cos{\theta}$ can 
be simplified to:

@@

Where the value of $A_{n}$ is the area of the first polygon, with $n=4$ sides, and as such 
$A_{n} = 4 \sin{45} \cos{45} = 2$. We can define: \\
$U_{0} = \cos{a} = \cos{45} = \frac{1}{\sqrt{2}}$ \\
$U_{1} = cos{\frac{\alpha}{2}}$ \\
Which we can, through the trigonometric identity 
$\cos^2{\theta} = \frac{1}{2} + \frac{1}{2} \cos{2\theta}$, simplify as
$U_{1} = \sqrt{\frac{1}{2} + \frac{1}{2} U_{0}}$ \\
So it can be said that $U_{n} = \sqrt{\frac{1}{2} + \frac{1}{2} U_{n - 1}}$, which leads to 
a fully defined expression for the value of pi:

$\pi = \frac{2}{\prod\limits_{k=0}^\infty U_{k}}, U_{0} = \frac{1}{\sqrt{2}}, U_{n} = \sqrt{\frac{1}{2} + \frac{1}{2} U_{n - 1}}$ \footnotemark

These expressions, when under a single expression result in the aforementioned formula with nested roots.

\footnotetext{where $\prod$ signifies a product. Similar expression to $\sum$ }
